Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-11 hpmoon-asoco.tex
Spell check

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily paralellizable, since they are
population-based and creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

@@

\subsection{Proposed methods}
In this paper we analyse several SLA algorithms we have
implemented by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
                                %Which methods? - JJ Fergu: clarifying
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

@@

%ZDT3
\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations. However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$). This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$. This problem does not appear when $L=2048$. Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}

>>>>

%2 COMPUTATION -> PARALLEL
This aspect of searching for non-dominated solutions, as well as, in
many cases, the size of the search space itself, implies a high demand
of computational time, leading to the proposal of parallel and distributed methods to solve them
\citep{Luna15Survey,Mukhopadhyay14Survey,Chavez15MO,Hidalgo16residualstress,KAUR2018183,XU2018268},
%3 ONE WAY IS TO USE MOEAS BECAUSE
one of which are evolutionary algorithms (EAs)
\citep{DBLP:series/ncs/EibenS15}. EAs are bio-inspired meta-heuristics
that can be effectively used to find nearly optimal solutions for
optimization problems and are easily parallelizable, since they are
population-based and creating a functionally equivalent parallel
version is as easy as distributing the population in communicating
computing nodes, which are usually called islands. The fact that
they are population-based helps find many solutions that compose the
Pareto front simultaneously.

@@

\subsection{Proposed methods}
In this paper we analyze several SLA algorithms we have
implemented by using a parallel multi-objective baseline algorithm
as a basis for comparisons. Our proposed methods, using different overlapping schemes, %methods or method?
                                %Which methods? - JJ Fergu: clarifying
are based on NSGA-II, as almost all the previous works discussed
before
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Deb03distributed,Xiao03specialized,Wang09parallel,Martens13asynchronous}. % This is SoA stuff - JJ FERGU: Yes, I added it here againg because a reviewer wasn't very attentive
Therefore, we have used a basic distributed NSGA-II algorithm without
overlapping sections as the baseline (B).

@@

%ZDT3
\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations. However, with $L=512$, the rightmost part of the obtained non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$). This explains why with this chromosome length, the SLA methods do not improve the results obtained by $B$. This problem does not appear when $L=2048$. Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}
